Appendix

### 2019-08-07 manuscript/appendix.Rmd
turn on specific figs for appendix

@@

```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
```

@@

```{r cdl_viewport, fig.cap = "CDL landuse cover in example IWS.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/cdl_viewport-1.pdf")
```

@@

```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/tptn_maps-1.pdf")
```

```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover. Line is 1:1 not regression.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
```

```{r nlcd-versus-cdl_map, fig.cap = "Comparison between NLCD (2011) ag and pasture against CDL (2010) specific crops.", warning=FALSE, echo = FALSE, eval = FALSE}
knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
```

```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/satellite-1.pdf")
```

>>>>

\pagebreak

```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/tptn_maps-1.pdf")
```

@@

```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
```

```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover. Line is 1:1 not regression.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
```

```{r nlcd-versus-cdl_map, fig.cap = "Comparison between NLCD (2011) ag and pasture against CDL (2010) specific crops.", warning=FALSE, echo = FALSE, eval = TRUE}
knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
```

```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/satellite-1.pdf")
```

```{r cdl_viewport, fig.cap = "CDL landuse cover in example IWS.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/cdl_viewport-1.pdf")
```

@@

@@
